---
title: "A Lightning Primer on Open Source Community Building"
author: "Danielle Robinson, Mozilla Science Fellow"
date: "6/2/2017"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How to build a community around your project?
[Teach-R Project](https://github.com/marcosvital/teach-R-project)
```{r fig.width=8, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/TeachR-contrib.png")
 grid.raster(img)
```

## How to build a community around your project?

- Writing good docs
- Communication and management
- Most people don't get trained in how to do this
- Also, it's hard to prioritize

## Mozilla Resources

- [Mozilla Open Leadership Training online materials](https://mozilla.github.io/open-leadership-training-series/)
- [A mentorship program](https://medium.com/@MozOpenLeaders/getting-ready-for-open-leadership-training-round-3-d7d0065f9c38)
- [Working Open Workshops](https://daniellecrobinson.github.io/mini-wow-pdx/)

```{r fig.align="center", fig.width=5, fig.height=4,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/miniWOWPDX-2017-group-pic.png")
 grid.raster(img)
```

## Open Leadership Training R Projects {.columns-2}
```{r fig.align="left", fig.width=4, fig.height=4,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/RRROBOTS.png")
grid.raster(img)
```

```{r fig.align="right", fig.width=4, fig.height=4,echo=FALSE}
library(png)
library(grid)
img <-readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/Teach-R.png")
grid.raster(img)
```

## One example
... and this might feel cheesy
```{r fig.align="center", fig.width=8, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/open_canvas_example.png")
 grid.raster(img)
```

## Less talk, more action
Want to learn more? Join me at [Open Source Bridge](http://opensourcebridge.org/attend/)
 for "microWorking Open Workshop (microWOW): Launch Your Open Project!" 6/21 10am-11:45

```{r fig.align="center", fig.width=8, fig.height=4,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/OS-Bridge-session.png")
 grid.raster(img)
```

## Thank you!
Stay in touch! 
@[daniellecrobins](https://twitter.com/daniellecrobins)
@[MozillaScience](https://twitter.com/MozillaScience)
```{r fig.width=4, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("~/Documents/Cascadia-R-conf-lightiningtalk/Mozilla-science-lab.png")
 grid.raster(img)
```
